### 2015-08-28 fundamentals/intro.tex
spell check

\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness
\cite{cohen_modern_2010,fagan_design_2002}, improves
the strength and quality of results through peer review
\cite{donoho_reproducible_2009,ince_case_2012,stodden_scientific_2010,wicherts_willingness_2011,petre_code_2014}, and
cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
being comprised of dynamically loadable, interchangeable, plug-in libraries of fuel cycle component
process physics that vary in their scope, depth, and fidelity. This modularity
allows users and developers to customise \Cyclus to analyze the cases that are
of interest to them rather than any custom application the simulator was
originally developed to address. Additionally, that customizability allows
useres and developers to address those cases at the level of fidelity necessary
for their application. The fundamental concepts of the \Cyclus
nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor, \gls{GENIUS} Version 1
\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, originated within
\gls{INL} and sought to provide generic regional capability.  Based on lessons
learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version 2
\cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The \Cyclus
project then improved upon the \gls{GENIUS} effort by implementing increased
modularity and encapsulation.  The result is a dynamic simulator that treats
both materials and facilities discretely, with an architecture that permits
multiple and variable levels of fidelity. Using an agent-based framework, the
simulator tracks the transformation and trade of resources between autonomous
regional and institutional entities with customizable behavior and
objectives. Each of these concepts (agent-based, resource tracking, and
regional as well as institutional entities) will be described in their own
sections (sections \ref{sec:abm}, \ref{sec:mats}, and \ref{sec:rif}
respectively).  Together, they provide a capability for extension and reus
beyond that pursued by any existing fuel cycle simulator.

>>>>

\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness
\cite{cohen_modern_2010,fagan_design_2002}, improves
the strength and quality of results through peer review
\cite{donoho_reproducible_2009,ince_case_2012,stodden_scientific_2010,wicherts_willingness_2011,petre_code_2014}, and
cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
being comprised of dynamically loadable, interchangeable, plug-in libraries of fuel cycle component
process physics that vary in their scope, depth, and fidelity. This modularity
allows users and developers to customise \Cyclus to analyze the cases that are
of interest to them rather than any custom application the simulator was
originally developed to address. Additionally, that customizability allows
users and developers to address those cases at the level of fidelity necessary
for their application. The fundamental concepts of the \Cyclus
nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor, \gls{GENIUS} Version 1
\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, originated within
\gls{INL} and sought to provide generic regional capability.  Based on lessons
learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version 2
\cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The \Cyclus
project then improved upon the \gls{GENIUS} effort by implementing increased
modularity and encapsulation.  The result is a dynamic simulator that treats
both materials and facilities discretely, with an architecture that permits
multiple and variable levels of fidelity. Using an agent-based framework, the
simulator tracks the transformation and trade of resources between autonomous
regional and institutional entities with customizable behavior and
objectives. Each of these concepts (agent-based, resource tracking, and
regional as well as institutional entities) will be described in their own
sections (sections \ref{sec:abm}, \ref{sec:mats}, and \ref{sec:rif}
respectively).  Together, they provide a capability for extension and reuse
beyond that pursued by any existing fuel cycle simulator.
